---
title: "Untitled"
author: "me!"
date: "6/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 2
### Q2.1
let-7g is family of miRNAs.
miRNAs are non-coding RNAs that are involved in post-transcriptional regulation of gene expression in organisms. They affect both the stability and translation of mRNAs.
dysregulation of let-7g is known to be a factor of several types of cancer, such as lung and breast cancer.
### Q2.2.1
The gene WDR82 overlaps let-7g.

### Q2.2.3
It is clrealy visible that the let-7g section is conserved very accuraetly through most species we checked, but the areas surrounding the let-7g are only conserved in apes.

### Q2.3.1
TP53 & AGO2 tend to co-occur.
AGO2 & MIR-34A tend to be mutually exclusive.
TP53 & MIR-34A tend to co-occur.

### Q2.3.2
The study we found is "The Role of TP53 in miRNA Loading Onto AGO2 and in Remodelling the miRNA–mRNA Interaction Network".
a cite from the study concerning TP53 & AGO2 tendency to co-occur:
"TP53 directly associated with AGO2, and induced and reduced loading of a subset of miRNAs, including the lethal 7 (let-7) miRNA family members, onto AGO2 in response to DNA damage."

### Q2.3.3
In the study "TP53 regulates miRNA association with AGO2 to remodel the miRNA–mRNA interaction network" the writers discuss the connection between the pair and the let-7 family:
"This revealed a significant TP53-dependent regulatory effect on the association between AGO2 and the entire let-7 family apart from let-7d (Fig. 2A), and we validated these findings by RT-qPCR (Fig. 2B,C)."






## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
